Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
removed outline text that now is actual content

\begin{itemize}
\item \sout{ evaluation [esp. automatic evaluation]}
\item \sout{popular current
  measures BLEU \cite{papineni02bleu}, TER}
\end{itemize}
Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system translation to
one or more reference (human) translations.
%
Automatic measures of this kind (e.g.\ BLEU \cite{papineni02bleu}) not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

@@

\begin{itemize}
\item \sout{challenges - motivate search for better measures}
\item \sout{other extensions:}
  \begin{itemize}
  \item \sout{METEOR }
    \begin{itemize}
    \item \sout{stemming and synonym tables}
    \item \sout{tuned but not generally     tuneable}
    \end{itemize}
  \item \sout{TERp}
    \begin{itemize}
    \item \sout{development-set tuning by user}
    \item \sout{stemming and synonym tables}
    \item \sout{paraphrase tables}
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \sout{prior work with (partial) syntactic locality:}
  \begin{itemize}
  \item \sout{Liu \& Gildea }
  \item \sout{Roark et al. Sparseval}
  \item \sout{Owczarzak et al. 2007}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \sout{Evaluation of evaluation measures}
  \begin{itemize}
  \item \sout{correlation vs. human fluency/adequacy }
  \item \sout{correlation vs. human-in-the-loop measures (HTER)}
  \end{itemize}
\end{itemize}

@@

Outline of big idea here.

\begin{itemize}
\item comparison of various bags of components of parse tree
  [ Figure describing Sparseval-ish variant ]

  Like sparseval: basic unit is labeled dependency pair

  Note: inbound links \& full pairs "overweight" head words; this is
  a good thing.

  [ figure demonstrating F-measure over d+l+h decomposition of toy
  trees ]

\item elements may be combined in various ways: single-bag F, combination of p,r
  measures (evenly, on analogy with BLEU)... or we might weight
  different combinations

\end{itemize}
\section{Experimental paradigm}
\label{sec:paradigm}

>>>>

Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system translation to
one or more reference (human) translations.
%
Automatic measures of this kind (e.g.\ BLEU \cite{papineni02bleu}) not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

@@

@@

@@

@@

\section{Experimental paradigm}
\label{sec:paradigm}
